Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-25 netsoft_paper.tex
update

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\subsection{Service Deployment Model}
With architecture mentioned in Fig. \ref{fig:desc_nfv_overview}, we come up with a network function service deployment model. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

@@

The infrastructure controller is a composed Docker \ref{seo2014}\ref{compare-vm-container} management server with the ability to manage the Docker resources like containers and images. The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.

>>>>

@@

\subsection{Service Deployment Model}
Different from some related works are discussed about virtualizing network functions located in PE devices \cite{vcpe-enhance}, we come up with a network function service deployment model, with architecture mentioned in Fig. \ref{fig:desc_nfv_overview}. Because computing infrastructures handles the algorithm and policies, and the generic network devices only do stateless processing, the customer just need to buy a general SDN switch at their home gateway and will have a different network function service by subscribing different the NFV controller through our vCPE platform.

@@

The infrastructure controller is a composed Docker management server with the ability to manage the Docker resources like containers and images \cite{seo2014}\cite{compare-vm-container}. The infrastructure doesn't handle the customer authentication or maintaining the state of running service, it just follows the request from the infrastructure orchestrator to create, delete, start, stop and inspect containers.
